COG-ED Manuscript

### 2022-01-24 06_Paper/COG-ED/Manuscript.Rmd
implemented CIs and effect sizes for contrasts

  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)

@@

  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)

@@

  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)

@@

@@

>>>>

  # get effect size and confidence interval

  hypothesis1a_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[1], df_error = hypothesis1a_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                     format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[2], df_error = hypothesis1a_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                     format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[3], df_error = hypothesis1a_contrasts$df[3], ci = 0.95), digits = 2)[1,1])

  hypothesis1a_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[1], df_error = hypothesis1a_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[2], df_error = hypothesis1a_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[3], df_error = hypothesis1a_contrasts$df[3], ci = 0.95), digits = 2)[1,2])

  # rename contrasts and column names

  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)

@@

  # get effect size and confidence interval

  hypothesis1b_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[1], df_error = hypothesis1b_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                     format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[2], df_error = hypothesis1b_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                     format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[3], df_error = hypothesis1b_contrasts$df[3], ci = 0.95), digits = 2)[1,1])

  hypothesis1b_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[1], df_error = hypothesis1b_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[2], df_error = hypothesis1b_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[3], df_error = hypothesis1b_contrasts$df[3], ci = 0.95), digits = 2)[1,2])

  # rename contrasts and column names

  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)

@@

  # get effect sizes and confidence intervals

  hypothesis1c_mental_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[1], df_error = hypothesis1c_mental_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[2], df_error = hypothesis1c_mental_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[3], df_error = hypothesis1c_mental_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[4], df_error = hypothesis1c_mental_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[5], df_error = hypothesis1c_mental_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[6], df_error = hypothesis1c_mental_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
  hypothesis1c_mental_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[1], df_error = hypothesis1c_mental_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[2], df_error = hypothesis1c_mental_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[3], df_error = hypothesis1c_mental_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[4], df_error = hypothesis1c_mental_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[5], df_error = hypothesis1c_mental_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[6], df_error = hypothesis1c_mental_contrasts$df[6], ci = 0.95), digits = 2)[1,2])

  hypothesis1c_physical_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[1], df_error = hypothesis1c_physical_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[2], df_error = hypothesis1c_physical_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[3], df_error = hypothesis1c_physical_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[4], df_error = hypothesis1c_physical_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[5], df_error = hypothesis1c_physical_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[6], df_error = hypothesis1c_physical_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
  hypothesis1c_physical_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[1], df_error = hypothesis1c_physical_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[2], df_error = hypothesis1c_physical_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[3], df_error = hypothesis1c_physical_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[4], df_error = hypothesis1c_physical_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[5], df_error = hypothesis1c_physical_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[6], df_error = hypothesis1c_physical_contrasts$df[6], ci = 0.95), digits = 2)[1,2])

  hypothesis1c_time_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[1], df_error = hypothesis1c_time_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[2], df_error = hypothesis1c_time_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[3], df_error = hypothesis1c_time_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[4], df_error = hypothesis1c_time_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[5], df_error = hypothesis1c_time_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[6], df_error = hypothesis1c_time_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
  hypothesis1c_time_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[1], df_error = hypothesis1c_time_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[2], df_error = hypothesis1c_time_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[3], df_error = hypothesis1c_time_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[4], df_error = hypothesis1c_time_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[5], df_error = hypothesis1c_time_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[6], df_error = hypothesis1c_time_contrasts$df[6], ci = 0.95), digits = 2)[1,2])

  hypothesis1c_effort_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[1], df_error = hypothesis1c_effort_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[2], df_error = hypothesis1c_effort_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[3], df_error = hypothesis1c_effort_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[4], df_error = hypothesis1c_effort_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[5], df_error = hypothesis1c_effort_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[6], df_error = hypothesis1c_effort_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
  hypothesis1c_effort_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[1], df_error = hypothesis1c_effort_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[2], df_error = hypothesis1c_effort_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[3], df_error = hypothesis1c_effort_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[4], df_error = hypothesis1c_effort_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[5], df_error = hypothesis1c_effort_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[6], df_error = hypothesis1c_effort_contrasts$df[6], ci = 0.95), digits = 2)[1,2])

  hypothesis1c_frustration_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[1], df_error = hypothesis1c_frustration_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[2], df_error = hypothesis1c_frustration_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[3], df_error = hypothesis1c_frustration_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[4], df_error = hypothesis1c_frustration_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[5], df_error = hypothesis1c_frustration_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[6], df_error = hypothesis1c_frustration_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
  hypothesis1c_frustration_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[1], df_error = hypothesis1c_frustration_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[2], df_error = hypothesis1c_frustration_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[3], df_error = hypothesis1c_frustration_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[4], df_error = hypothesis1c_frustration_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[5], df_error = hypothesis1c_frustration_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[6], df_error = hypothesis1c_frustration_contrasts$df[6], ci = 0.95), digits = 2)[1,2])

  hypothesis1c_performance_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[1], df_error = hypothesis1c_performance_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[2], df_error = hypothesis1c_performance_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[3], df_error = hypothesis1c_performance_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[4], df_error = hypothesis1c_performance_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[5], df_error = hypothesis1c_performance_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[6], df_error = hypothesis1c_performance_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
  hypothesis1c_performance_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[1], df_error = hypothesis1c_performance_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[2], df_error = hypothesis1c_performance_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[3], df_error = hypothesis1c_performance_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[4], df_error = hypothesis1c_performance_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[5], df_error = hypothesis1c_performance_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[6], df_error = hypothesis1c_performance_contrasts$df[6], ci = 0.95), digits = 2)[1,2])

  # rename columns and contrasts

  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)

@@

Effect size and confidence interval:

$\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,2]`

Bayes factor:

@@

Effect size and confidence interval:

$\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,2]`

Bayes factor:
